---
title: '\Climate, Twitter Retweet: Is there an Relationship?'
author: "Kelton, Xiaoshen and Sune"
date: ''
output:
  html_document: default
  pdf_document:
    fig_caption: yes
bibliography: null
link-citations: yes
csl: plos.csl
abstract: This is an abstract.
---

<!--TO-DO
- add state FIPS, replace clustering factor in LFE FELM models with State (instead of county) FIPS
- analysis(counts, emotions for TMAX, PRCP for County and Cell level outcomes)
- plots(counts, emotions for TMAX, PRCP for County and Cell level outcomes)
- writeup 
- tables
- generate/devise four figures (including county level climate forecast of # of days with TMAX over 30C for next 100 years)

Run from command line to generate RMarkdown:

Rscript -e "rmarkdown::render(".../climate_twitter_volume_Xiaoshen.Rmd")"
-->

```{r opts, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
chooseCRANmirror(graphics=FALSE, ind=1)
knitr::opts_chunk$set(fig.path='figures/', warning=F, message=F, fig.retina=NULL, cache=T, cache.lazy=F, autodep=T, echo=F, eval=T)

```

```{r packages server}
#Install relevant packages
#install.packages("bit64", "/mnt/opt/miniconda2/envs/my-r-env/bin/R/library")
#install.packages("ggthemes", "/mnt/opt/miniconda2/envs/my-r-env/bin/R/library")
#install.packages("sandwich", "/mnt/opt/miniconda2/envs/my-r-env/bin/R/library")
#install.packages("lmtest", "/mnt/opt/miniconda2/envs/my-r-env/bin/R/library")
#install.packages("ggmap", "/mnt/opt/miniconda2/envs/my-r-env/bin/R/library")
#install.packages("ggplot2", "/mnt/opt/miniconda2/envs/my-r-env/bin/R/library")
#install.packages("Hmisc", "/mnt/opt/miniconda2/envs/my-r-env/bin/R/library")
#install.packages("RColorBrewer", "/mnt/opt/miniconda2/envs/my-r-env/bin/R/library")
#install.packages("grid", "/mnt/opt/miniconda2/envs/my-r-env/bin/R/library")
#install.packages("MASS", "/mnt/opt/miniconda2/envs/my-r-env/bin/R/library")
#install.packages("gplots", "/mnt/opt/miniconda2/envs/my-r-env/bin/R/library")
#install.packages("lfe", "/mnt/opt/miniconda2/envs/my-r-env/bin/R/library")
#install.packages("stargazer", "/mnt/opt/miniconda2/envs/my-r-env/bin/R/library")
#install.packages("lubridate", "/mnt/opt/miniconda2/envs/my-r-env/bin/R/library")
#install.packages("zoo", "/mnt/opt/miniconda2/envs/my-r-env/bin/R/library")
#install.packages("reshape2", "/mnt/opt/miniconda2/envs/my-r-env/bin/R/library")
#install.packages("maptools", "/mnt/opt/miniconda2/envs/my-r-env/bin/R/library")
#install.packages("dplyr", "/mnt/opt/miniconda2/envs/my-r-env/bin/R/library")
#install.packages("plyr", "/mnt/opt/miniconda2/envs/my-r-env/bin/R/library")
#install.packages("data.table", "/mnt/opt/miniconda2/envs/my-r-env/bin/R/library")
#install.packages("caTools", "/mnt/opt/miniconda2/envs/my-r-env/bin/R/library")
#install.packages("ncdf4", "/mnt/opt/miniconda2/envs/my-r-env/bin/R/library")
#install.packages("stringr", "/mnt/opt/miniconda2/envs/my-r-env/bin/R/library")
#install.packages("knitr", "/mnt/opt/miniconda2/envs/my-r-env/bin/R/library")
#install.packages("pander", "/mnt/opt/miniconda2/envs/my-r-env/bin/R/library")
#install.packages("rasterVis", "/mnt/opt/miniconda2/envs/my-r-env/bin/R/library")
#install.packages("GGally", "/mnt/opt/miniconda2/envs/my-r-env/bin/R/library")
#install.packages("matrixStats", "/mnt/opt/miniconda2/envs/my-r-env/bin/R/library")
#install.packages("ggExtra", "/mnt/opt/miniconda2/envs/my-r-env/bin/R/library")
#install.packages("gridExtra", "/mnt/opt/miniconda2/envs/my-r-env/bin/R/library")
#install.packages("viridis", "/mnt/opt/miniconda2/envs/my-r-env/bin/R/library")
#install.packages("devtools", "/mnt/opt/miniconda2/envs/my-r-env/bin/R/library")
#install.packages("cowplot", "/mnt/opt/miniconda2/envs/my-r-env/bin/R/library")
#install.packages("captioner", "/mnt/opt/miniconda2/envs/my-r-env/bin/R/library")
```


```{r packages R studio}
#Install relevant packages
#install.packages("bit64")
#install.packages("ggthemes")
#install.packages("sandwich")
#install.packages("lmtest")
#install.packages("ggmap")
#install.packages("ggplot2")
#install.packages("Hmisc")
#install.packages("RColorBrewer")
#install.packages("grid")
#install.packages("MASS")
#install.packages("gplots")
#install.packages("lfe")
#install.packages("stargazer")
#install.packages("lubridate")
#install.packages("zoo")
#install.packages("reshape2")
#install.packages("maptools")
#install.packages("dplyr")
#install.packages("plyr")
#install.packages("data.table")
#install.packages("caTools")
#install.packages("ncdf4")
#install.packages("stringr")
#install.packages("knitr")
#install.packages("pander")
#install.packages("rasterVis")
#install.packages("GGally")
#install.packages("matrixStats")
#install.packages("ggExtra")
#install.packages("gridExtra")
#install.packages("viridis")
#install.packages("devtools")
#install.packages("cowplot")
#install.packages("captioner")
#install.packages("ordinal")

#Load packages
library(bit64) # long integers
library(ggthemes) #themes for plotting
library(sandwich) #robust se estimator
library(lmtest) #lm functions
library(ordinal) #ologit funcitons
library(memisc) #import stata data
library(ggmap) #make nice plots with ggplot mapping
library(ggplot2) #nice plots
library(Hmisc) #multipurpose package
library(RColorBrewer) #make nice colors
library(grid) #plotting package
library(MASS) #multipurpose package
library(gplots) #nice plotting
library(lfe) #run linear fixed effects models
library(stargazer) #output nice tables
library(lubridate) #deal with dates
library(zoo) #deal with dates
library(reshape2) #powerful reshape package
library(sp) #general spatial class package
library(gstat) #geostat package
library(spacetime) #store data in proper spatial/temporal class
library(raster) #convert to raster and vice versa
library(maptools) #plot and modify shapefiles
library(rgeos) #for use with maptools for shapefiles
library(rgdal) #for reading in shapefiles
library(RSAGA) #needed for spatial downscaling
library(RCurl) #also needed for spatial downscaling
library(dplyr) #for data frame manipulation functions
library(plyr) #for additional manipulation functions
library(data.table) #for data.table functions
library(foreign) #for reading in .dta files
library(parallel) #for parallel processing functions
library(caTools) #functions for fast running mean and sd
library(stringr) #string tools
library(knitr) #knitting
library(pander) #pandering
library(rasterVis) # plotting rasters
library(GGally) # for correlation plots
library(geosphere) # spherical distance
library(Rcpp) # for C++
library(RcppArmadillo) # for C++ (and Conley errors)
library(matrixStats) # matrix calculations
#library(ggExtra) # for marginal histograms
#library(gridExtra) # for multiplots
#library(viridis) # for colors
#library(Cairo) # pdf device
#library(gtable) # for gtable filter
library(devtools)
#install.packages("cowplot")
#devtools::install_github("wilkelab/cowplot")
library(cowplot)
library(captioner)

#install.packages("stargazer") #Use this to install it, do this only once
library(stargazer)

library(arm)

# set cores for parallel processing
#registerDoMC()
```

```{r functions}
# functions for grabbing p-values and coefficients from summaries of felm models
coef <- function(reg, name) {
    if (round(reg$coefficients[rownames(reg$coefficients)==name, 1], 3) == 0) {
        format(round(reg$coefficients[rownames(reg$coefficients)==name, 1], 4), scientific=FALSE) 
    }
    else round(reg$coefficients[rownames(reg$coefficients)==name, 1], 3)
}
pval <- function(reg, name) {
  if (round(reg$coefficients[rownames(reg$coefficients)==name, 4], 3) >=0.001) 
  {round(reg$coefficients[rownames(reg$coefficients)==name, 4], 3)} 
  else paste("< 0.001")
}

# captioner setting
fig_num <- captioner()
tab_num <- captioner(prefix="Table")
eq_num <- captioner(prefix="Equation")
sfig_num <- captioner(prefix="Figure S", auto_space=FALSE)
stab_num <- captioner(prefix="Table S", auto_space=FALSE)
seq_num <- captioner(prefix="Equation S", auto_space=FALSE)

# bin plot function
source("binned_plot_function.R")
```

```{r data}
getwd()
#A <- read.csv("US_2016_25KMbinned.csv", header = TRUE, as.is = TRUE)
#B <- read.csv("US_2015_25KMbinned.csv", header = TRUE, as.is = TRUE)
#C <- read.csv("US_2014_25KMbinned.csv", header = TRUE, as.is = TRUE)
#D <- read.csv("US_2013_25KMbinned.csv", header = TRUE, as.is = TRUE)

#A <- read.csv("US_2016_county.csv", header = TRUE, as.is = TRUE)
#B <- read.csv("US_2015_county.csv", header = TRUE, as.is = TRUE)
#C <- read.csv("US_2014_county.csv", header = TRUE, as.is = TRUE)
#D <- read.csv("US_2013_county.csv", header = TRUE, as.is = TRUE)

A <- read.csv("US20_integrated.csv", header = TRUE, as.is = TRUE)
#B <- read.csv("US_2015_EMO_county.csv", header = TRUE, as.is = TRUE)
#C <- read.csv("US_2014_EMO_county.csv", header = TRUE, as.is = TRUE)
#D <- read.csv("US_2013_EMO_county.csv", header = TRUE, as.is = TRUE)

#merge dataframes
climatweet_df <- A
summary(climatweet_df)
```

```{r variables}

#create year and month variable
climatweet_df$year <- substr(climatweet_df$timestamp,1,4)
min(climatweet_df$year)

#create cityindexxmonthxyr variable
cols <- c("idx", "month", "year")
climatweet_df$cellmnyr <- do.call(paste, c(climatweet_df[cols], sep="-"))

#replace count_daily_urban and count_daily_rural "NA" values with zero 
climatweet_df$count_tweet[is.na(climatweet_df$count_tweet)] <- 0
str(climatweet_df$count_tweet)

#only include rows without missing values
climatweet_df<-na.omit(climatweet_df)

#create variables for ratio_daily_city
climatweet_df$ratio_daily_cell <- climatweet_df$count_tweet
climatweet_df$nratio_daily_cell <- climatweet_df$nratio

#create climate variables for each city
climatweet_df$TMAX_cell <- climatweet_df$TMAX

climatweet_df$TMIN_cell <- climatweet_df$TMIN

climatweet_df$CC_cell <- climatweet_df$CC

climatweet_df$HUM_cell <- climatweet_df$HUM

climatweet_df$PRCP_cell <- climatweet_df$PRCP
  
climatweet_df$WIND_cell <- climatweet_df$WIND

##Change the scale of PRCP from MM to CM
climatweet_df$PRCP_cell <- climatweet_df$PRCP_cell/10

#convert all categorical variables into factors
climatweet_df$year <- as.factor(climatweet_df$year)
climatweet_df$calendardate <- as.factor(climatweet_df$timestamp)
climatweet_df$cellxmn <- as.factor(climatweet_df$cellmnyr)
climatweet_df$idx <- as.factor(climatweet_df$idx)

#create trange climate variables for PRISM
climatweet_df$TRANGE_cell <- (climatweet_df$TMAX_cell - climatweet_df$TMIN_cell)

#create climate factor variables, cuts, and set reference categories 
climatweet_df$CUTTMAX_cell <- cut(climatweet_df$TMAX_cell, breaks=c(-Inf,seq(0, 30, by=5),40)) 
climatweet_df$CUTTMAX_cell <- relevel(climatweet_df$CUTTMAX_cell, ref="(20,25]")

climatweet_df$CUTTRANGE_cell <- cut(climatweet_df$TRANGE_cell, breaks=c(-Inf,seq(0, 35, by=5),Inf)) 
climatweet_df$CUTTRANGE_cell <- relevel(climatweet_df$CUTTRANGE_cell, ref="(0,5]")

climatweet_df$CUTTPRCP_cell <- cut(climatweet_df$PRCP_cell, breaks=c(-Inf,seq(0, 10, by=1),Inf)) 
climatweet_df$CUTTPRCP_cell <- relevel(climatweet_df$CUTTPRCP_cell, ref="(-Inf,0]")

climatweet_df$CUTTWIND_cell <- cut(climatweet_df$WIND_cell, breaks=c(-Inf,seq(0, 25, by=5),Inf)) 
climatweet_df$CUTTWIND_cell <- relevel(climatweet_df$CUTTWIND_cell, ref="(0,5]")

climatweet_df$CUTTCC_cell <- cut(climatweet_df$CC_cell, breaks=c(-Inf,seq(0, 100, by=20),Inf)) 
climatweet_df$CUTTCC_cell <- relevel(climatweet_df$CUTTCC_cell, ref="(0,20]")

climatweet_df$CUTTHUM_cell <- cut(climatweet_df$HUM_cell, breaks=c(-Inf,seq(0, 100, by=20),Inf)) 
climatweet_df$CUTTHUM_cell <- relevel(climatweet_df$CUTTHUM_cell, ref="(40,60]")

#create log transformed outcome
climatweet_df$ratio_daily_cell_log <- log10(climatweet_df$ratio_daily_cell)
climatweet_df$nratio_daily_cell_log <- log10(climatweet_df$nratio_daily_cell)

```


```{r}

#check levels

levels(climatweet_df$CUTTMAX_cell)
levels(climatweet_df$CUTTPRCP_cell)
levels(climatweet_df$CUTTRANGE_cell)
levels(climatweet_df$CUTTCC_cell)
levels(climatweet_df$CUTTHUM_cell)
levels(climatweet_df$CUTTWIND_cell)
```


<!-- some dummy text and code below -->

```{r}
# captioner
LABEL_ME <- fig_num(name = "LABEL_ME", caption = "")
```

```{r}
str(climatweet_df)
#summary(climatweet_df$monthly_cell_count_rural)
#create subset of data with summer months
#climatweet_df_>10countsmonth <- subset(climatweet_df, (month=="6" | month=="7" | month=="8"))
```

```{r}

coefplot(flex_t_cell, predictors="CUTTMAX", coefficients=c("(Intercept)", "color.Q"), strict=TRUE)
```


```{r LABEL_ME, dev='jpeg', dpi=300, fig.height=6.5, fig.width=6.5, fig.cap="\\textbf{Spatial and temporal variation} This figure depicts the US grid cells and counties covered by each of our data sources. Panel (a) plots... Panel (b) shows... Panel (c) illustrates ... Panel (d) shows... ."}
#####################################################

# insert the code to generate your plots here. change the fig.cap above accordingly.

# flex_t_cell model
flex_t_cell <- felm(formula = climatweet_df$ratio_daily_cell_log ~ CUTTMAX_cell + 
                                          CUTTPRCP_cell + 
                                          CUTTRANGE_cell + 
                                          CUTTCC_cell + 
                                          CUTTHUM_cell + 
                                          CUTTWIND_cell 
                | calendardate + cellxmn 
                | 0 
                | idx, 
                data = climatweet_df, na.action = na.omit) 

summary(flex_t_cell)

vnames = row.names(flex_t_cell$coefficients)
# plot flex_t_cell model
flex.plot <- binned.plot(felm.est = flex_t_cell,
                 plotvar = "CUTTMAX_cell",
                 breaks = 5,
                 omit = c(20,25),
                 linecolor = "blue4",
                 pointfill = "blue4",
                 errorfill = "blue4",
                 xlabel = "Max. Temperature in C",
                 ylabel = "Ratio"
                 )
hist <- axis_canvas(flex.plot, axis = "x") + geom_histogram(data = climatweet_df, aes(x = climatweet_df$TMAX_cell), bins=10, fill='blue4', color='gray60', alpha=0.75, size=0.1)
flex.plot <- insert_xaxis_grob(flex.plot, hist, position = "bottom", height = grid::unit(0.1, "null"))
flex.plot <- ggdraw(flex.plot)
flex.plot

flex.plot <- binned.plot(felm.est = flex_t_cell,
                 plotvar = "CUTTPRCP_cell",
                 breaks = 1,
                 omit = c(0,0),
                 ylimit = c(0,0.08),
                 #xlimit = c(0,6),
                 roundx = 1,
                 linecolor = "red4",
                 pointfill = "red4",
                 errorfill = "red4",
                 xlabel = "Precipitation in cm",
                 ylabel = "Ratio"
                 )
hist <- axis_canvas(flex.plot, axis = "x") + geom_histogram(data = climatweet_df, aes(x = climatweet_df$PRCP_cell), bins=20, fill='red4', color='gray60', alpha=0.75, size=0.1)
flex.plot <- insert_xaxis_grob(flex.plot, hist, position = "bottom", height = grid::unit(0.1, "null"))
flex.plot <- ggdraw(flex.plot)
flex.plot



```

To explore if outside weather conditions alter tweeting behavior, we use tweets in the continguous United States between 2013 and 2016 (see `r fig_num("LABEL_ME", display="cite")`a). We include data from counties with less than thirty days of zero tweets in total. 

We combine this twitter data -- marked by day and geolocated to the county level -- with meteorological data from two sources. The PRISM Climate Group, provides gridded (at ~4km) daily maximum and minimum temperatures (in Celsius) as well as daily sumtotal precipitation (in millimeters) for the continental US [@di2008constructing]. The second source, the National Centers for Environmental Prediction (NCEP) Reanalysis II project, provides gridded daily average cloudcover, average relative humidity, and average wind speed over the same period [@kanamitsu2002ncep]. 

Our theoretical relationship of interest is the effect of weather conditions on the log number of tweets in a given county on a given day. We empirically model this relationship as:

```{r}
fe <- eq_num(name = "fe", caption = "")
```

$$Y_{ijtm} = f(TMAX_{ijtm}) + g(PRECIP_{ijtm}) + \textbf{Z}\boldsymbol{\eta} + \alpha_i + \mu_t + \nu_{jm} + \epsilon_{ijtm} \ \ \ \ \ (1)$$

In this time-series cross-sectional model, $i$ indexes counties, $j$ indexes states, $t$ indexes calendar days, and $m$ indexes calendar months. Our dependent variable $Y_{ijtm}$ corresponds to the log number of tweets in county $i$ in state $j$ on calendar day $t$ within calendar month $m$. Our independent variables of interest are maximum daily temperature, $TMAX_{ijtm}$, and daily precipitation, $PRECIP_{ijtm}$. We also control for temperature range, percentage cloud cover, relative humidity, and average wind speed, represented via $\textbf{Z}\boldsymbol{\eta}$, as failure to do so may bias our estimates of the effect of maximum temperatures and precipitation on the log number of tweets. We include $\alpha_i$ -- representing county indicator variables -- in `r eq_num("fe", display="cite")`. We also include $\mu_t$ and $\nu_{js}$ in `r eq_num("fe", display="cite")`, representing calendar date and state-by-calendar month indicator variables, respectively to control for other confounds. 

Following the climate econometrics literature [@hsiang2016econometrics;@hsiang2017estimating], our empirical identifying assumption is that the remaining variation in daily maximum temperature and precipitation is as good as random after conditioning on these fixed effects. Hence, the estimated model coefficients from $f(TMAX_{ijtm})$ and $g(PRECIP_{ijtm})$ can be interpreted as the causal effects of maximum temperature and precipitation on the log number of tweets in a county-day.

We estimate `r eq_num("fe", display="cite")` using ordinary least squares and adjust for possible spatial and serial correlation in $\epsilon_{ijtm}$ by employing heteroskedasticity-robust standard errors clustered at the state level [@greene2003econometric]. We omit non-climatic control variables from `r eq_num("fe", display="cite")` because of their potential to generate bias in our parameters of interest [@hsiang2013quantifying;@acharya2016explaining;@hsiang2016econometrics]. 
